R for Clinical Study Reports and Submission

### 2021-11-17 tlf-ae-summary.Rmd
fix minor typos

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to the number of participants were included in each safety analysis in Section 12.2, Adverse Events (AEs).

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need the number of participants were included in each safety analysis in Section 12.2, Adverse Events (AEs).

### 2021-11-17 tlf-disposition.Rmd
fix minor typos

In this chapter, we show how to the create a typical disposition table.

@@

The first step is to read in the relevant datasets into R.
For a disposition table, all the required information is saved in a Subject-level Analysis Dataset (ADSL).
This dataset is provided in `sas7bdat` format, which is a SAS data format currently used in many clinical trial analysis and report.
The `haven` package is able to read the dataset, while maintaining its attributes (e.g., variable labels).

>>>>

In this chapter, we show how to create a typical disposition table.

@@

The first step is to read in the relevant datasets into R.
For a disposition table, all the required information is saved in a Subject-level Analysis Dataset (ADSL).
This dataset is provided in `sas7bdat` format, which is a SAS data format currently used in many clinical trial analysis and reporting.
The `haven` package is able to read the dataset, while maintaining its attributes (e.g., variable labels).

### 2021-11-17 tlf-overview.Rmd
fix minor typos

There are also books to introduce tidyverse.
We assume the reader to have experience in using `tidyverse` in this book.

@@

We provide a brief introduction of `r2rtf` and showe how to transfer
data frames into table, listing, and figures (TLFs).

@@

`r2rtf` support 26 different border types. The details can be found on
the [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type).

>>>>

There are also books to introduce tidyverse.
We assume the reader have experience in using `tidyverse` in this book.

@@

We provide a brief introduction of `r2rtf` and show how to transfer
data frames into table, listing, and figures (TLFs).

@@

`r2rtf` supports 26 different border types. The details can be found on
the [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type).
